\sysfull

### 2018-04-11 paper/intro.tex
cleancut and intel paper added to bib (Brandon: intelehcompiler ->baghsorkhi_cgo_2018)

%Moved intel note to related work
\textbf{Task Decomposition of Intermittent Programs.} {\em
Task-based} programming and execution models require a
programmer~\citep{alpaca,chain} or a compiler~\cite{intelehcompiler} to
statically decompose a program into a collection of {\em tasks}.  A task can
include arbitrary computation and these existing systems guarantee that each
tasks executes {\em atomically}, despite arbitrarily-timed power failures.  
%
The programmer explicitly expresses task-to-task control flow, or the compiler
converts existing program control-flow into task-to-task control flow to sequence 
the tasks that it defines.
%
Figure~\ref{fig:coalesce} (top) illustrates how a program's tasks execute and
shows how tasks can impose a run-time overhead. 
%
At each task transition, the system incurs an overhead to track and atomically
commit modifications to the non-volatile memory, to maintain consistency of
program state~\citep{chain,alpaca}.  
%
The more task transitions a program executes at run time, the more overhead.

>>>>

%Moved intel note to related work
\textbf{Task Decomposition of Intermittent Programs.} {\em
Task-based} programming and execution models require a
programmer~\citep{alpaca,chain} or a compiler~\cite{baghsorkhi_cgo_2018} to
statically decompose a program into a collection of {\em tasks}.  A task can
include arbitrary computation and these existing systems guarantee that each
tasks executes {\em atomically}, despite arbitrarily-timed power failures.  
%
The programmer explicitly expresses task-to-task control flow, or the compiler
converts existing program control-flow into task-to-task control flow to sequence 
the tasks that it defines.
%
Figure~\ref{fig:coalesce} (top) illustrates how a program's tasks execute and
shows how tasks can impose a run-time overhead. 
%
At each task transition, the system incurs an overhead to track and atomically
commit modifications to the non-volatile memory, to maintain consistency of
program state~\citep{chain,alpaca}.  
%
The more task transitions a program executes at run time, the more overhead.
